A statistical assessment of influenza intensity thresholds from the moving epidemic and WHO methods

### 2023-07-10 Draft/Draft_MEM.tex
Updating draft.

@@

For our re-sampling scheme we use publicly available data on the weekly incidence of influenza-like illness per 100,000 inhabitants in France, 1985--2019, as published by Réseau Sentinelles (INSERM/Sorbonne Université, \url{https://www.sentiweb.fr}, \citealt{Flahault2006}). These are available both at the national and at a regional level. To make statements about the sensitivity and specificity of the ``very high'' categorization, we require a larger set of historical data than the available 35 seasons. We therefore pool curves from the 12 continental French administrative regions. As the overall level of ILI incidences varies considerably across regions, we scale all data such that the average season peak per region is 100. As the data from the Corse island region differ substantially from the other regions, with overall considerably lower reported incidences, we exclude them. Moreover, all curves from the pandemic 2009/2010 season were removed. In total we then dispose of 408 historical seasons.

@@

Materials to reproduce the presented results are available at \url{https://github.com/jbracher/mem}.

>>>>

\bigskip

\begin{quote}
\textbf{Keywords:} calibration, influenza, intensity threshold, moving epidemic method, re-sampling, sensitivity, WHO method.
\end{quote}

@@

For our re-sampling scheme we use publicly available data on the weekly incidence of influenza-like illness per 100,000 inhabitants in France, 1986--2019, as published by Réseau Sentinelles (INSERM/Sorbonne Université, \url{https://www.sentiweb.fr}, \citealt{Flahault2006}). These are available both at the national and at a regional level. To make statements about the sensitivity and specificity of the ``very high'' categorization, we require a larger set of historical data than the available 35 seasons. We therefore pool curves from the 12 continental French administrative regions. As the overall level of ILI incidences varies considerably across regions, we scale all data such that the average season peak per region is 100. As the data from the Corse island region differ substantially from the other regions, with overall considerably lower reported incidences, we exclude them. Moreover, all curves from the pandemic 2009/2010 season were removed. In total we then dispose of 396 historical seasons.

@@

Materials to reproduce the presented results are available at \url{https://github.com/jbracher/mem_who}.
